---
title: 'Bayesian FE & RE NMA using PWE model (via gemtc package) - Result Generation'
author: "Sandro Gsteiger"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bayesian FE & RE NMA using PWE model (via gemtc package) - Result Generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(ggplot2)
library(R2jags)
library(ggmcmc)
library(gemtcPlus)

rsd <- 29348
do.conv.diag <- TRUE
```


# Inputs

```{r}
# Grouped survival data
data("grouped_KM")
```


__Figure__ Binned Kaplan-Meier curves (digitized and in-house data)
```{r, echo=FALSE, fig.width=11, fig.height=8}
ggplot(data = grouped_KM) +
  geom_step(aes(t.start, S.start)) +
  facet_grid(study ~ treatment) +
  ylim(0, 1) +
  xlab("Month") +
  ylab("Survival probability")
```


# Run the NMA

## NMA input data

Add numeric study and treatment identifiers (with treatments ordered to have suitable NMA reference).
```{r}
ref.std <- "STUDY2"                # select study (for baseline estimates)
nma.ref.trt <- "B"                 # need to select well connected treatment as nw ref


# START PRE PROC FNC HERE

cut.points <- c(3, 10)

dat <-  nma_pre_proc(dat = grouped_KM,
                     data.type = "GSD",
                     nma.ref.trt = nma.ref.trt,
                     ref.std = ref.std,
                     cut.pts = cut.points
                     )

  
head(dat, 10)
tail(dat, 10)
```


Generate numeric arm identifiers, numbers of arms per study, .
```{r}
# Prepare input data: counters for arm etc

dat_jags <- nma_jags_inits(dat = dat)

d_std <- dat_jags$d_std
d_arms <- dat_jags$d_arms
d_trts <- dat_jags$d_trts

# dat has been modified (join inside `nma_jags_inits` to include columns `arm` and `n_arms`
dat <- dat_jags$dat

rm(dat_jags)
```


Input data for JAGS.
```{r}
dat_jg <- list(
  Nobs = nrow(dat),
  Ns = nrow(d_std),
  Na = d_std$n_arms,
  segment = dat$segment,
  Ncuts = length(cut.points),
  r = dat$n.event,
  n = dat$n.risk,
  dt = dat$dt,
  s = dat$studyn,
  a = dat$arm,
  t = as.matrix(select(ungroup(d_trts), -studyn)),
  Ntrt = max(select(ungroup(d_trts), -studyn), na.rm = TRUE)
)
dat_jg # pre-proc output

# END DATA PRE-PROC HERE
```


## JAGS fits

```{r}
## output object needed for each fit
out_gen <- list(r.seed = rsd,
                data.jg = dat_jg,
                data.df = dat,
                data.arms = d_arms,
                model.type = "PWE",
                model.pars = list(cut.pts = cut.points))
out_all <- list()
```

```{r}
fit.count <- 0
```

### Fixed effect model

```{r, echo=TRUE}
n.iter <- 5000   # TOO SMALL FOR REAL ANALYSIS
n.burnin <- 2500 # MORE PRACTICAL FOR EXAMPLE
n.thin <- 1
n.chains <- 3


# COMBINE jags and dic.samples call into one function

# JAGS fit
set.seed(rsd)
rm(fit)
fit <- jags(model.file = system.file("BUGScode",
                                     "tte_piece-wise-cst_fe.txt",
                                     package = "gemtcPlus"),
            data = c(dat_jg,
                     list(prior_mean = 0),
                     list(prior_prec = 0.0001)),
            parameters = c("d", "mu"),
            n.chains = n.chains,
            n.iter = n.iter,
            n.burnin = n.burnin,
            n.thin = n.thin)


fit.count <- fit.count + 1

# Re-calculate DIC as default in JAGS uses normal approximation instead of full MCMC samples
DICsamp <- dic.samples(fit$model, n.iter = n.iter, n.burn = n.burnin, thin = n.thin, type="pD")
DICsamp

fit$BUGSoutput$DIC      <- sum(DICsamp$deviance) + sum(DICsamp$penalty)
fit$BUGSoutput$pD       <- sum(DICsamp$penalty)
fit$BUGSoutput$DICbyR   <- FALSE

fit
```


```{r}
## Diagnostics
if (do.conv.diag) {get_pwe_conv_diag(fit,
                                     file = here::here("inst", "extdata", "results", paste("fit-pwe-conv-", fit.count, ".pdf", sep = "")))}

## prepare output
out_all[[fit.count]] <- c(out_gen,
                          list(fit = fit,
                               DICsamp = DICsamp,
                               descr_s = "PWE, FE",
                               descr = "Piecewise exponential model (fixed effect)",
                               RE = FALSE,
                               comment.re = NA,
                               prior = NA)
)
```




### Random effects models

__Informative prior by Turner et al. LN(-4.2, 1.4^2)__
```{r, echo=TRUE}
set.seed(rsd)
rm(fit)
fit <- jags(model.file = system.file("BUGScode",
                                     "tte_piece-wise-cst_re_lnprior.txt",
                                     package = "gemtcPlus"),
            data = c(dat_jg,
                     list(prior_mean = 0),
                     list(prior_prec = 0.0001),
                     list(ln.prior.mn = -4.18),
                     list(ln.prior.prec = 1/1.41^2)),
            parameters = c("d", "mu", "sd"),
            n.chains = n.chains, n.iter = n.iter, n.burnin = n.burnin, n.thin = n.thin)
fit.count <- fit.count + 1

# Re-calculate DIC as default in JAGS uses normal approximation instead of full MCMC samples
DICsamp <- dic.samples(fit$model, n.iter = n.iter, n.burn = n.burnin, thin = n.thin, type="pD")
DICsamp

fit$BUGSoutput$DIC      <- sum(DICsamp$deviance) + sum(DICsamp$penalty)
fit$BUGSoutput$pD       <- sum(DICsamp$penalty)
fit$BUGSoutput$DICbyR   <- FALSE

fit
```


```{r}
## Diagnostics
if (do.conv.diag) {get_pwe_conv_diag(fit,
                                     file = here::here("inst",
                                                       "extdata",
                                                       "results",
                                                       paste("fit-pwe-conv-",
                                                             fit.count,
                                                             ".pdf",
                                                             sep = "")))}

## prepare output
out_all[[fit.count]] <- c(out_gen,
                          list(fit = fit,
                               DICsamp = DICsamp,
                               descr_s = "PWE, RE (Turner et al prior)",
                               descr = "Piecewise constant model (random effects, Turner et al prior LN(-4.2, 1.4^2))",
                               RE = TRUE,
                               comment.re = "Informative prior (Turner et al, LN(-4.2, 1.4^2))",
                               prior = "LN(-4.2, 1.4^2)"))
```


__Inflated Turner et al. prior LN(-2, 1.4^2)__
```{r, echo=TRUE}
set.seed(rsd)
rm(fit)
fit <- jags(model.file = system.file("BUGScode",
                                     "tte_piece-wise-cst_re_lnprior.txt",
                                     package = "gemtcPlus"),
            data = c(dat_jg,
                     list(prior_mean = 0),
                     list(prior_prec = 0.0001),
                     list(ln.prior.mn = -2),
                     list(ln.prior.prec = 1/1.4^2)),
            parameters = c("d", "mu", "sd"),
            n.chains = n.chains, n.iter = n.iter, n.burnin = n.burnin, n.thin = n.thin)
fit.count <- fit.count + 1

# Re-calculate DIC as default in JAGS uses normal approximation instead of full MCMC samples
DICsamp <- dic.samples(fit$model, n.iter = n.iter, n.burn = n.burnin, thin = n.thin, type="pD")
DICsamp

fit$BUGSoutput$DIC      <- sum(DICsamp$deviance) + sum(DICsamp$penalty)
fit$BUGSoutput$pD       <- sum(DICsamp$penalty)
fit$BUGSoutput$DICbyR   <- FALSE

fit
```


```{r}
## Diagnostics
if (do.conv.diag) {get_pwe_conv_diag(fit,
                                     file = here::here("inst",
                                                       "extdata",
                                                       "results",
                                                       paste("fit-pwe-conv-",
                                                             fit.count,
                                                             ".pdf",
                                                             sep = "")))}

## prepare output
out_all[[fit.count]] <- c(out_gen,
                          list(fit = fit,
                               DICsamp = DICsamp,
                               descr_s = "PWE, RE (Inflated Turner et al prior)",
                               descr = "Piecewise constant model (random effects, Inflated Turner et al prior, LN(-2, 1.4^2))",
                               RE = TRUE,
                               comment.re = "Inflated Turner et al prior, LN(-2, 1.4^2))",
                               prior = "LN(-2, 1.4^2)"))
```


__Save output object for report generation.__
```{r, echo=TRUE}
# split list into separate objects, otherwise file size too large for github (>100MB)
for(i in seq_along(out_all)){
  out <- out_all[[i]]
  save(out, file = here::here("inst",
                              "extdata",
                              "results",
                              paste("fit-pwe-",
                                    i,
                                    ".RData",
                                    sep = "")))
}
```


# Session info
```{r}
date()
sessionInfo()
```

